\section{Future Changes}
\label{sec:future_changes}
\begin{itemize}
  \item Use of the whistle for fouls in general. This would being able to successfully identify and isolate whistle tones from a referee on the field, sounds around the field, and other whistle sounds being made within the RoboCup competition venue. This can be a tough challenge, especially as whistles used by referees can be quite varied,
  \item Use spoken referee commands during gameplay. This would allow the robots to start to interpret the referee direction and reduce the dependence on the GameController computer. RoboCup Soccer will need to move further in this direction to reach the 2050 goal. This is likely to be initially introduced as a technical challenge.
  \item Add Arc to the Penalty Box. This would be the final change for the field to model human-soccer, and allow the rules to more closely approximate to those of human-soccer for penalty shots. This has been left out due to the challenge of accurately constructing arcs and circles compared to straight lines.
  \item Any Ball, if the technical requirements goes beyond training artificial networks. The TC view it as an uninteresting technical requirement to have teams re-train their networks for a new ball on site. It simply adds to the stress of competition without producing any meaningful research. However, if use of different balls is constructed in a manner to bring new and interesting research challenges beyond training networks, this is of interest.
\end{itemize}

\subsection{Roadmap}

\todo{Add table from Rudi}