% !TeX root = ../SPL-Rules.tex
% !TeX spellcheck = en_US
\section{Introduction}

%Since RoboCup 2021 will be held virtually around the world, owing to the ongoing COVID-19 situation and the Standard Platform League is taking on a new form that is designed to provide all teams an opportunity to competitively measure their skills in robot soccer within the current circumstances without any physical presence on a common competition site. Also, other local opens have been cancelled.
We plan to organize GORE 2.0 (GermanOpen Replacement Event) from the 3rd till 6th of February 2022 as a follow-up event to the GORE and want to offer remote 5 vs 5 games which were not possible for the last years. We plan to host games in designated two central arenas in Europe. 
No travel to competition sites or other teams venues will be necessary for human team members for this competition, but four of your robots have to travel.

Due to a probably dense timetable, we will only offer a few time slots for testing technical challenges for the RoboCup 2022.

Live-streaming of videos will be incorporated into the event to keep the contact between teams alive as well as presenting an entertaining experience for the public and sponsors.

GORE asks teams to compete by remotely deploying their code onto robots at a neutral arena (also the hosting teams), which is an important step towards facilitating fully remote soccer games. The rules and the guidance for referees have been designed to ensure the safe operation and protection of robot hardware in all arenas.

\subsection{Code of Honor}

We believe that all teams act fair during competition. Thus, we ask all participants to acknowledge a Code of Honor.
\begin{enumerate}
    \item The safe operation of the robots is paramount, especially where teams deploy remote their software onto robots owned by other teams. Referees and participants should act to prevent damage to robots, and be proactive in enforcing rules  designed to minimize damage.
    \item Teams should endeavour to install bug-free and conservative software for remote games. Also, remote games feature elements of speed, there are strict consequences for damaging robots, and we hope no team will be prevented from competing due to these reasons.
    \item This is no official RoboCup game. Still, teams want to win the games and be the winner of GORE 2.0 but play these games more in the sense of a test game. Winning is \textbf{not} everything.
    \item In case a team detects malfunction robot during setup, teams can agree a replacement of this.
    \item MAC-Address of LAN adapter remains unchanged during the event.
\end{enumerate} 

It is our experience that SPL teams are extremely gracious and congenial, and we expect that the Code of Honor will be honored. However, violation of this code may result in immediate disqualification.

\subsection{Registration}

If you want to participate in this event, please write an email until the \textbf{15th of December 2021} to the organisers with the following content:
\begin{itemize}
    \item Team Name
    \item Contact person name and email
    \item Commitment to participate
    \item Can and do you want to provide a host arena?
    \item How many V6 NAOs (at least 4) do you want sent to a host arena?
    \item Do you comply to the Code of Honor?
    \item Providing return address for robots.
\end{itemize}

\subsection{Key dates}

\begin{itemize}[leftmargin=*,labelsep=0.7cm, labelindent=2cm]
    \item [2021-12-\phantom{15}] Rules for GORE\_2
    \item [2021-12-15] Commitment to participate
    \item [2021-12-15] Commitment to host an arena
    \item [2021-12-20] Confirmation for participants and hosting arenas
    \item [2022-01-24] Submission of credentials for arena access
    \item [2022-01-24] Arena network access contact
    \item [2022-01-24] Sending robots to hosting arenas
    \item [2022-01-24] Fill our robot id data
    \item [2022-02-03] field\_dimensions.json available
    \item [2022-02-03] Upload images of the field
    \item [2022-02-03] Welcome, setup day
    \item [2022-02-04] Competition Day 1
    \item [2022-02-05] Competition Day 2
    \item [2022-02-06] Competition Day 3
    \item [2022-02-08] Return robots back to teams
\end{itemize}
