% !TeX root = ../SPL-Challenges.tex
% !TeX spellcheck = en_US
\section{Data Minimization Challenge} % TODO: I hope there is a better name for this challenge
This challenge will take place throughout all matches of the main competition and the score will be based on the quantity of bytes exchanged by active robots during matches. 


\subsection{Challenge Goal}
The purpose of this challenge is to reward good network data usage strategies that minimize the number of bytes sent by each active robot. Both the quantity of exchanged bytes and the uptime of active robots will be taken into consideration when computing the score.

\subsection{Challenge Scoring}
Network data usage will be evaluated by keeping track of the ratio $R$ between the cumulative count of bytes sent by all active robots in the team and the total uptime of robots in the team for SPL match $m$:

$$ R^\text{m} = \frac{\sum_{i}^n b_i}{\sum_{i}^n t_i} $$

where:
\begin{itemize}
    \item $b_i$ is the number of bytes sent by robot $i$
    \item $t_i$ is the uptime of robot $i$, defined as the time during which robot $i$ is playing and is not penalized.
\end{itemize}
The sum takes into account all robots that were at some point active during the match, therefore also correctly taking into account substitutions and penalizations.

An average $R^\text{m}$ is computed for each match. The final score $A^\text{t}$ for team $t$ is the average over all matches disputed by that team:

$$ A^\text{t} = \frac{1}{M} \left( \sum_{m}^M R^\text{m} \right) $$

where:
\begin{itemize}
    \item $M$ is the number of matches played by team $t$
\end{itemize}


The objective of each team in this challenge is to minimize the average $A^t$.

\subsection{Exclusion from challenge}
Being an in-game challenge, all teams participating in the main competition will automatically take part in this challenge if they score at least one goal during the whole duration of the preliminary tournament phase.

\subsection{Code publication}
Teams are exempted from publishing code related to this challenge, as it may involve a full code publication. Even if it is not mandatory, teams are still encouraged to publish code related to this in-game challenge in some measure.
