% !TeX root = ../SPL-Rules.tex
% !TeX spellcheck = en_US
\section{Changes From \LastRCYear}

This is a brief non-normative list of rule changes from \LastRCYear to \RCYear:
\begin{itemize}
  \item The \texttt{ready} visual signal and the corresponding delay
        also apply to Challenge Shield as well as Champions Cup.
        (\cref{sec:robot_states})
  \item The \texttt{ready} signal delay is increased to
        \qty{\ReadyDelayTimeChampion}{\second} for Champions Cup and to
        \qty{\ReadyDelayTimeChallenge}{\second} for Challenge Shield.
        (\cref{sec:robot_states})
  \item The \texttt{Motion in Standby} penalty for falsely detecting the
        \texttt{ready} visual signal now results in a team wide penalty,
        but for a shorter duration. (\cref{sec:motion_in_standby})
  \item Team communication packets sent during \texttt{standby} now count
        against the team's message budget for the game. (\cref{sec:wireless})

  \item The kicking team for free kicks in Champions Cup matches is communicated
        via visual referee signal. The GameController no longer shares this
        information in those games. (\cref{sec:free_kick_gesture})
  \item If a team fails to execute a free kick, the opposing team
        may attempt to score directly. (\cref{sec:indirect_kick_default})

  \item 2024 Champion Cup Indirect Kick rules now apply to Challenge Shield as well.
        Challenge Shield teams have a fallback option available to them if they
        are unable to field enough robots. (\cref{sec:indirect_kick_default})

  \item Drop ball rule: in special situations where it can't be determined
        which team should have kickoff, neither team gets any special right
        to play the ball first. (\cref{sec:drop_ball_rule})
  \item Penalty abortion: penalties can now be aborted early in case they were
        erroneously assigned by the referee. (\cref{sec:aborting_penalty})
  \item Ball stop rule: each half of the game can be allowed to last
        a little longer to let the attack situation finish. (\cref{sec:early_stopping})
\end{itemize}
